---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# workflowr2

<!-- badges: start -->
<!-- badges: end -->

The goal of workflowr2 is to take data that overviews the number and status of customer appointments along with data of technician workflow and analyze them together and provide visuals.

## Installation

You can install the released version of workflowr2 from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("workflowr2")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(workflowr2)
## basic example code which shows the average total vehicle seen on a Monday in the shop
MeanAppt(ApptData$MonT)
```

## Plot Example 

This shows a box and whisker plot detailing the average amount of cars we have seen and the high and low extremes over a seven month period.

```{r echo=FALSE}
TotalT_V <- ApptData[,32]
TotalT_DF <- data.frame(TotalT_V)
boxplot(TotalT_DF,
        main = "Total Vehicles Seen",
        ylab = "Vehicles Seen")
```
